---
title: "Mumbai Metro Map"
author: "Akash Mer"
date: "`r Sys.Date()`"
output:
    html_document:
        keep_md: true
        code_folding: hide
        theme: readable
        highlight: espresso
knit: (function(input, ...){
    rmarkdown::render(input,
        output_dir = "C:/Users/akash/Documents/datasciencecoursera/Mumbai_Metro_Map/docs",
        output_file = file.path("./index"))
    })
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```


```{r map, warning=FALSE, message=FALSE, fig.cap="Refernce: Location Data obtained form Google Maps and icons obtained and edited from https://icon-library.com/icon/subway-icon-2.html", fig.align='center', fig.height=6, fig.width=10}
# Loading the required packages
if(system.file(package = "leaflet") == "") install.packages("leaflet")
library(leaflet)

# Loading in the data
datLoc <- read.csv("./data/stationLocs.csv", header = TRUE)
datNames <- read.csv("./data/stationNames.csv", header = TRUE)
dat <- cbind(datNames,datLoc)

# Reading in the icons
red <- makeIcon("./data/red.png", iconWidth = 31*215/250, iconHeight = 25,
                    iconAnchorX = 31*215/250/2, iconAnchorY = 16)
yellow <- makeIcon("./data/yellow.png", iconWidth = 31*215/250, iconHeight = 25,
                    iconAnchorX = 31*215/250/2, iconAnchorY = 16)
pink <- makeIcon("./data/pink.png", iconWidth = 31*215/250, iconHeight = 25,
                    iconAnchorX = 31*215/250/2, iconAnchorY = 16)

# Creating the icon list
iconSet <- iconList(red = red, yellow = yellow, pink = pink)

# Creating the map 
metro_map <- leaflet(dat) %>%
    addTiles() %>%
    addMarkers(~long, ~lat, popup = ~station,
               labelOptions = labelOptions(textsize = "px"),
               icon = ~iconSet[line]) %>%
    addLegend(labels = c("Line 1(Pink Line)", "Line 2A(Yellow Line)",
                         "Line 7(Red Line)"),
              colors = c("magenta", "yellow", "red"))

# Displaying the map
metro_map
```
  
# **APPENDIX**

## **Kindly download and unzip the following [files](https://github.com/AkashMer/Mumbai_Metro_Map/blob/main/data/data.zip) before reproducing this example** Alternatively you can download the *data* subdirectory from the this [repository](https://github.com/AkashMer/Mumbai_Metro_Map)

## **R markdown details**
  
Written in **Rmarkdown file in `r R.version.string` using RStudio IDE**  
**Packages** used for this report,  
  
* **leaflet** : *Version `r packageVersion("leaflet")`*
  
**Creation Date of Rmarkdown file :** `r file.info("./scripts/index.Rmd")$ctime`  
**Last Modified Date of Rmarkdown file :** `r file.info("./scripts/report.Rmd")$mtime`